%%%%%%%%%%%%%%%%%%%%%%% file template.tex %%%%%%%%%%%%%%%%%%%%%%%%%
%
% This is a general template file for the LaTeX package SVJour3
% for Springer journals.          Springer Heidelberg 2010/09/16
%
% Copy it to a new file with a new name and use it as the basis
% for your article. Delete % signs as needed.
%
% This template includes a few options for different layouts and
% content for various journals. Please consult a previous issue of
% your journal as needed.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%


%
\RequirePackage{fix-cm}

% unfortunately, we need this hack for cleref with svjour3
\makeatletter
\def\cl@chapter{}
\makeatother

%
%\documentclass{svjour3}                     % onecolumn (standard format)
\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
%\documentclass[smallextended]{svjour3}       % onecolumn (second format)
%\documentclass[twocolumn]{svjour3}          % twocolumn
%
\smartqed  % flush right qed marks, e.g. at end of proof
%

\input{preamble}    % for useful commands
\input{notation}    % should be rather exchangeable

\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{stmaryrd,amsmath,amssymb}
\usepackage{listings}
\usepackage{xcolor}
\usepackage[capitalise,noabbrev]{cleveref}
\usepackage{times}
%\usepackage{courier}
\lstdefinelanguage{MiniZinc}
{
	morekeywords={array,solve,constraint,let,tuple,diff,function,repeat,union,where,exists,set,min,max,float,int,var,predicate,minimize,sum,in,forall,include,to,card,if,then,else,endif,print,search}, 
	sensitive=false,
	morecomment=[l]{\%},
	morecomment=[s]{/*}{*/},
	morestring=[b]",
}

\definecolor{lightlightgray}{gray}{0.99}
\definecolor{forestgreen}{HTML}{009B55}
\definecolor{thermicred}{rgb}{0.82, 0.1, 0.26}

\lstset
{
	basicstyle={\ttfamily\fontsize{7pt}{8pt}\selectfont},
	commentstyle=\ttfamily\color{forestgreen},
	stringstyle=\ttfamily\color{thermicred},
	keywordstyle=\ttfamily\bfseries\color{blue},
	tabsize=2,
	showstringspaces=false,
	stepnumber=5,
	numberfirstline=false,
	%flexiblecolumns=true,
	firstnumber=1,
	numbers=left,
	captionpos=b,	
	backgroundcolor=\color{lightlightgray},
	frame=single,
	%xleftmargin=\parindent,
	numberstyle={\ttfamily\fontsize{6pt}{6pt}\selectfont}
}

\lstset{language=MiniZinc}
%
\usepackage{mathptmx}      % use Times fonts if available on your TeX system
%
% insert here the call for the packages your document requires
%\usepackage{latexsym}
% etc.
%
% please place your own definitions here and don't use \def but
% \newcommand{}{}
%
% Insert the name of "your journal" with
% \journalname{myjournal}
%
\begin{document}

\title{Qualitative Soft Constraints\thanks{This research is partly sponsored by the 
German Research Foundation (DFG) in the project ``OC-Trust'' (FOR 1085).}
}
%\subtitle{Do you have a subtitle?\\ If so, write it here}

%\titlerunning{Short form of title}        % if too long for running head

\author{Alexander Schiendorfer \and Alexander Knapp \and Wolfgang Reif %etc.
}

%\authorrunning{Short form of author list} % if too long for running head

\institute{Alexander Schiendorfer \at
              University of Augsburg\\
              \email{schiendorfer@isse.de}           %  \\
%             \emph{Present address:} of F. Author  %  if needed
           \and
           Alexander Knapp \at
           University of Augsburg\\
              \email{knapp@isse.de}   
           \and
           Wolfgang Reif \at
           University of Augsburg\\
              \email{reif@isse.de}  
}

\date{Received: date / Accepted: date}
% The correct dates will be entered by the editor


\maketitle

% This is not the actual abstract (much too boring)
% but should serve as a rough outline
\begin{abstract}
Over-constrained problems are ubiquitous in industrial and other real-world problems.
Plenty of formalisms have been proposed and abstracted in algebraic structures.
Specialized areas diverged such as cost function networks or semiring-based soft constraints.
Integration with conventional constraint problems are implemented using soft global constraints.
Most of them involve a cost variable / cost functions. This is not good, if costs can be defined
by different agents/modelers that lack a common currency idea. We propose a formalism that is purely 
qualitative, relies on the satisfaction/dissatisfaction of soft constraints. Preferences are written
as a directed acyclic graph. We show how to proceed from this graph by suggesting set orderings over
sets of violated constraints, prove that these orderings are mathematically enforced by common axioms
of monoidal soft constraints, discuss the relationship to other formalisms in terms of expressiveness,
implement various optimization strategies using MiniZinc/MiniSearch, and provide experimental results.

\keywords{Soft Constraints \and Over-constrained Problems \and Modeling Formalisms \and MiniZinc}
\end{abstract}

\section{Introduction}
\label{sec:introduction}
\input{introduction}

\section{Related Work}
\label{sec:related-work}
\input{related-work}

\section{Foundations}
\label{sec:foundations}
\input{foundations}
% -----------------------
\section{Implementation}
\label{sec:implementation}
\input{implementation}
% -----------------------

\section{Evaluation}

\section{Conclusion}

%\begin{acknowledgements}
%If you'd like to thank anyone, place your comments here
%and remove the percent signs.
%\end{acknowledgements}

% BibTeX users please use one of
%\bibliographystyle{spbasic}      % basic style, author-year citations
\bibliographystyle{spmpsci}      % mathematics and physical sciences
%\bibliographystyle{spphys}       % APS-like style for physics
\bibliography{constraint-preferences}   % name your BibTeX data base

\end{document}
% end of file template.tex

