\subsection{Tailoring MiniZinc to Accomodate Softness}
Here we'll have a short introduction into how we actually 
modeled our benchmark problems. Includes how we added several
notions of constraints, different levels (few: 3-5, medium: 5-10, many: 10+)

What are the aspects that need motivation?
\begin{enumerate}
\item Enhanced propagation by redundant constraints
\item Search heuristics
\item Comparing BaB with LNS (depending on MiniSearch's progress)
\end{enumerate}

\begin{enumerate}
\item \textbf{Factors}: type of heuristics / variable ordering, enhanced propagation
\item \textbf{Dependent Variables}: runtime / failures / nb. problems solved / optimal value after 5 minutes
\end{enumerate}

\subsection{Overhead from Softness}

Here, we'll compare the plain MiniZinc problems with softened but more constrained problems.
Central question: How much harder / slower will it be to find (optimal) solutions?
We shall, of course, present the altered models online! Including some documentation about
how we modified the original problems.

\begin{enumerate}
\item Measure if a problem that was easy in the beginning is still easy
\item Measure if hard problems get tremendously harder (play a bit with search heuristics)
\end{enumerate}

\subsection{Comparison with Related Work}

Here, we'll demonstrate that we do not really have a competing product, since no solver
truly implements algebraic structures for soft constraints. So nothing is
really offered in a qualitative setting.

But in the quantitative realm (with all its disadvantages), there are two competing solvers that 
offer bespoke solutions for weighted CSP. Even though we do not want to really compete in
terms of runtime, we hope to see the differences

\begin{enumerate}
\item WSimply 
\item Toulbar2, perhaps interfaced by Numberjack
\end{enumerate}

\todo[inline]{Figure out workflow of WSimply with MiniZinc models -- that'd be ideal!}
\todo[inline]{Try a model with Numberjack}
\todo[inline]{Find a cool scheduling/packing problem involving lots of global constraints 
and make a translation to WCSP/Numberjack Format for toulbar2}

